---
title: "optimism - plots"
author: "ML"
date: "7/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
sessionInfo()
options(scipen=100)
pacman::p_load(devtools, tidyverse, magrittr, fulltext, rotl, ape, dplyr, tidyr, rotl, fulltext, metafor, car, ggplot2, gridExtra, patchwork)
#install.packages("devtools")
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", force = TRUE, build_vignettes = TRUE) #vignette builder 'R.rsp' not found
#install.packages("R.rsp")
#install.packages("prettyunits")
library(orchaRd)

#source("../functions/functions.R")
```

```{r load data models, eval=TRUE, include=FALSE}
rm(list=ls()) # clean up

# loading data and tree
dat <- read.csv("./data/MA_dataset_with_ES_subsets.csv") #full data set
tree <- read.tree(file="./data/tree_all.tre")

#MA models sunsets
load(file = "./Rdata/MA_all.Rdata")
load(file = "./Rdata/MA_amb.Rdata")
load(file = "./Rdata/MA_MID_ES.RData")
load(file = "./Rdata/MA_maxabsES.Rdata")
load(file = "./Rdata/MA_maxmeanES.RData")
load(file = "./Rdata/MA_maxES.RData")
load(file = "./Rdata/MR_all_species.Rdata") #species model

#univariate MA models - full data set
load(file = "./Rdata/MR_all_sex1.Rdata")
load(file = "./Rdata/MR_all_MeasureType1.Rdata")
load(file = "./Rdata/MR_all_TaskType1.Rdata")
load(file = "./Rdata/MR_all_CueTypeCat1.Rdata")
load(file = "./Rdata/MR_all_ReinforcementCat1.Rdata")
load(file = "./Rdata/MR_all_AmbigReinforced1.Rdata")
load(file = "./Rdata/MR_all_WithinBetween1.Rdata")
load(file = "./Rdata/MR_all_ScalePoint1.Rdata")
load(file = "./Rdata/MR_all_source1.Rdata") 
load(file = "./Rdata/MR_all_age1.Rdata")
load(file = "./Rdata/MR_all_AffectManipCat1.Rdata")
load(file = "./Rdata/MR_all_AffectManipTiming1.Rdata")
load(file = "./Rdata/MR_all_ComparisonCategory1.Rdata")
load(file = "./Rdata/MR_all_FoodDeprived1.Rdata")
load(file = "./Rdata/MR_all_Automated1.Rdata")
load(file = "./Rdata/MR_all_Blind1.Rdata")

#full models
#load(file = "./Rdata/MR_Full_0.Rdata")
#load(file = "./Rdata/MR_Full_0_ambES.Rdata")
#load(file = "./Rdata/MR_Full_0_MID_ES.Rdata")
#load(file = "./Rdata/MR_Full_0_max_absES.Rdata")
#load(file = "./Rdata/MR_Full_0_MID_ES.Rdata")
#load(file = "./Rdata/RdataMR_Full_0_max_ES.Rdata")
```


### Figure 4. MA models for full data and 4 data subsets

```{r MA - orchard plot, eval=TRUE, include=FALSE}
#res1 <- mod_results(MA_all, mod = "Int")
#print(res1)
#orchard_plot(MA_all, mod = "Int", xlab = "Standardised mean difference", transfm = "none")

p1 <- orchard_plot(MA_all, xlab = "", transfm = "none", alpha = 0.3) +
xlim(-4,9)+ scale_y_discrete(labels = c(Intrcpt = "Overall"))  + scale_fill_manual(values = "grey") + scale_colour_manual(values = "grey") + theme(legend.position = "none") + ggtitle("a.  All data")  #"All data"

p2 <- orchard_plot(MA_amb, xlab = "", transfm = "none", alpha = 0.3) +
xlim(-4,9) + scale_y_discrete(labels = c(Intrcpt = "Overall")) + scale_fill_manual(values = "grey") + scale_colour_manual(values = "grey") + theme(legend.position = "none") + ggtitle("b.  Ambiguous cues data") #"Ambiguous cues data"

p3 <- orchard_plot(MA_MID_ES, xlab = "", transfm = "none", alpha = 0.3) +
xlim(-4,9) + scale_y_discrete(labels = c(Intrcpt = "Overall")) + scale_fill_manual(values = "grey") + scale_colour_manual(values = "grey") + theme(legend.position = "none") + ggtitle("c.  Mid-ambiguous cues data") #"Mid-ambiguous cues data"

p4 <- orchard_plot(MA_maxabsES, xlab = "", transfm = "none", alpha = 0.3) +
xlim(-4,9) + scale_y_discrete(labels = c(Intrcpt = "Overall")) + scale_fill_manual(values = "grey") + scale_colour_manual(values = "grey") + theme(legend.position = "none") + ggtitle("d.  Maximum absolute response data") # "Maximum absolute response data"

p5 <- orchard_plot(MA_maxmeanES, xlab = "", transfm = "none", alpha = 0.3) +
xlim(-4,9) + scale_y_discrete(labels = c(Intrcpt = "Overall")) + scale_fill_manual(values = "grey") + scale_colour_manual(values = "grey") + theme(legend.position = "none") + ggtitle("e.  Maximum response in dominant direction data") #"Maximum response in dominant direction data"

#p6 <- orchard_plot(MA_maxES, xlab = "Standardised mean difference [Hg]", transfm = "none", alpha = 0.25) +
#xlim(-4,9) + scale_y_discrete(labels = c(Intrcpt = "Overall")) + scale_fill_manual(values = "grey") + scale_colour_manual(values = "grey") + ggtitle("f.  Maximum positive response data") #"Maximum positive response data"

p1/p2/p3/p4/p5 #/p6

ggsave("plots/Figure4_Rplot.pdf", width = 16, height = 16, units = "cm", dpi = 300, scale=2)

#+ theme(legend.position = c(0.6, 1), legend.justification = c(0, 1), legend.key.size = unit(1, "mm")) + theme(legend.direction = "horizontal", legend.title = element_text(size = 8), legend.text = element_text(size = 8))
```


### Figure 5. MR model for full data with species identity as moderator 

```{r MA - orchard plot, eval=FALSE, include=FALSE}
#DONT USE
#res1 <- mod_results(MR_all_species, mod = "Species")
#print(res1)
p <- orchard_plot(MR_all_species, mod = "Species", xlab = "Standardised mean difference [Hg]", transfm = "none", alpha = 0.25, angle = 45,) + scale_fill_manual(values = rep("grey", 22)) + scale_colour_manual(values = rep("grey", 22))  + theme(legend.position = "none")
p
#need a way to re-order the species!
```

# phylogeny + traditional forest plot - USE

```{r species plot with phylogeny, eval=TRUE, include=TRUE}
### PLOT - species phylogeny and forest plot v2 (narrower)
ssp <- MR_all_species
load("./Rdata/MA_all.Rdata")
#gsub("ScientificName","",rownames(summary(MR_all_species)$b))
res_species_df <- data.frame(Model = substr(attr(ssp$b,"dimnames")[[1]], 15, 50), M = ssp$b, CI.lb = ssp$ci.lb, CI.ub = ssp$ci.ub, I2=NA, pch=20)
res_species_df <- res_species_df[match(tree$tip.label, res_species_df$Model), ] #reorder dataframe to match order of the tip labels on the tree
res_species_df$Signif <- ifelse(res_species_df$CI.lb>0 | res_species_df$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
count_animals <- data.frame(Model=names(table(dat$Species_Latin)), k=table(dat$Species_Latin)) #count how many ES per species
merged_res_species_df <- merge(res_species_df, count_animals, all=FALSE, sort=FALSE)
tab <- read.csv("./tables/table_included_papers_2019.csv")
table(tab$Species)
count_papers <- data.frame(Model=names(table(tab$Species)), K=table(tab$Species)) #count how many papers per species
merged_res_species_df2 <- merge(merged_res_species_df, count_papers, all=FALSE, sort=FALSE)
merged_res_species_df2 <- rbind(merged_res_species_df2, data.frame(Model=c("Meta-analytic mean "), M=MA_all$b[1], CI.lb=MA_all$ci.lb[1], CI.ub=MA_all$ci.ub[1], I2=NA, pch=18, Signif="", k.Var1 = NA, k.Freq=sum(merged_res_species_df2$k.Freq), K.Var1=NA, K.Freq=sum(merged_res_species_df2$K.Freq)))
write.csv(merged_res_species_df2,"tables/MR_species_res.csv")

pdf(file="plots/Figure5_species.pdf",width=6.5,height=6.5,pointsize=11)
layout(matrix(c(1,2),1), c(1,3), c(1,3))
par(mar=c(5.2,1,3.1,0))
plot(tree, font=1, cex=0.8, x.lim=1, show.tip.label = FALSE)
par(mar=c(4,7,1,0))
plot(merged_res_species_df2$M, 1:length(merged_res_species_df2$M), ylab=NA, yaxt="n", bty="n", xlim=c(-4,4), ylim=c(0.25, length(merged_res_species_df2$M)+.5), xlab="Standardised mean difference [Hg]", pch=merged_res_species_df2$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(merged_res_species_df2$Model[1:length(merged_res_species_df2$Model)], 2, -1, at=1:length(merged_res_species_df2$Model), las=2, cex=.8, font=3)
#mtext(merged_res_species_df2$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(merged_res_species_df2$CI.lb, 1:length(merged_res_species_df2$M), merged_res_species_df2$CI.ub, 1:length(merged_res_species_df2$M), lwd=1.25)
for (i in 1:length(rownames(merged_res_species_df2))) mtext(merged_res_species_df2$Signif[i], 2, -1.5, at=i, las=2, cex=.7) #add stars
mtext(merged_res_species_df2$k.Freq, 4, -2.8, at=1:(length(merged_res_species_df2$k.Freq)), las=2, cex=.8, font=1, adj=1) #add k values
mtext(merged_res_species_df2$K.Freq, 4, -1.4, at=1:(length(merged_res_species_df2$K.Freq)), las=2, cex=.8, font=1, adj=1) #add K values
mtext("k", 4, -2.8, at=length(merged_res_species_df2$k.Freq)+1, las=2, cex=.8, font=1, adj=1)
mtext("K", 4, -1.4, at=length(merged_res_species_df2$K.Freq)+1, las=2, cex=.8, font=1, adj=1)
dev.off()

#NOTE: fine edit plot formatting in AdobeIllustrator (add pictograms)
```


### Figure 6. MR models - univariate

```{r MA - orchard plot, eval=TRUE, include=FALSE}
#res1 <- mod_results(MR_all_sex1, mod = "Int")
#print(res1)
#orchard_plot(MR_all_sex1, mod = "Int", xlab = "Standardised mean difference [Hg]", transfm = "none", alpha = 0.25)

## 16 univariate models:
# MR_all_Sex1
# MR_all_MeasureType1
# MR_all_TaskType1
# MR_all_CueTypeCat1
# MR_all_ReinforcementCat1
# MR_all_AmbigReinforced1
# MR_all_WithinBetween1
# MR_all_ScalePoint1
# MR_all_source1 
# MR_all_age1
# MR_all_AffectManipCat1
# MR_all_AffectManipTiming1
# MR_all_ComparisonCategory1
# MR_all_FoodDeprived1
# MR_all_Automated1
# MR_all_Blind1

p1 <- orchard_plot(MR_all_sex1, mod = "Sex", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) + scale_y_discrete(labels = c("Female", "Male", "Mixed-sex"))  + scale_fill_manual(values = rep("grey",3)) + scale_colour_manual(values = rep("grey",3)) + theme(legend.position = "none") + ggtitle("a.  Sex")

p2 <- orchard_plot(MR_all_MeasureType1, mod = "Measurement type", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) + scale_y_discrete(labels = c("Latency", "Proportion"))  + scale_fill_manual(values = rep("grey",2)) + scale_colour_manual(values = rep("grey",2)) + theme(legend.position = "none") + ggtitle("b.  Measurement type")

p3 <- orchard_plot(MR_all_TaskType1, mod = "Task Type", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("Active choice", "Go/no-go"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("c.  Task type")

p4 <- orchard_plot(MR_all_CueTypeCat1, mod = "Cue Type", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("Auditory", "Olfactory", "Spatial", "Tactile", "Visulal"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("d.  Cue type")

p5 <- orchard_plot(MR_all_ReinforcementCat1, mod = "Reinforcement scheme", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("Reward vs. Null", "Reward vs. Punishement", "Reward vs. smaller Reward"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("e.  Reinforcement scheme") 

p6 <- orchard_plot(MR_all_AmbigReinforced1, mod = "Ambiguous cue reinforcement scheme", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("No", "Yes"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("f.  Ambiguous cue reinforced") 

p7 <- orchard_plot(MR_all_WithinBetween1, mod = "Study design", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("Between", "Within"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("g.  Within or between-individual study design") 

p8 <- orchard_plot(MR_all_ScalePoint1, mod = "Cue location", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("MID", "N", "NN", "NP", "P"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("h.  Cue type/location") 

p9 <- orchard_plot(MR_all_source1, mod = "Source", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("Captive", "Wild-caught"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("i.  Source of animals") 

p10 <- orchard_plot(MR_all_age1, mod = "Age", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("Adult", "Juvenile"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("j.  Age class of animals") 

p11 <- orchard_plot(MR_all_AffectManipCat1, mod = "AffectManipCat", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("Enrichment", "Stress"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("k.  Affect manipulation type") 

p12 <- orchard_plot(MR_all_AffectManipTiming1, mod = "AffectManipTiming", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("Just before/during", "Long-term"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("l.  Affect manipulation  timing") 

p13 <- orchard_plot(MR_all_ComparisonCategory1, mod = "ComparisonCategory", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("Benign-Worse", "Better-Benign", "Better-Worse"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("m.  Treatment comparison type") 

p14 <- orchard_plot(MR_all_FoodDeprived1, mod = "FoodDeprived", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("No", "Yes"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("n.  Testing food deprived animals") 

p15 <- orchard_plot(MR_all_Automated1, mod = "Automated", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("No", "Yes"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("o.  Automated behaviour measurements") 

p16 <- orchard_plot(MR_all_Blind1, mod = "Blind", xlab = "", transfm = "none", alpha = 0.25, angle = 0) +
xlim(-4,9) +  scale_y_discrete(labels = c("No", "Yes"))  + scale_fill_manual(values = rep("grey",5)) + scale_colour_manual(values = rep("grey",5)) + theme(legend.position = "none") + ggtitle("p.  Blinded behaviour measurements")

#p1 + p2 + p3 + p4 + p5 + p6 + p7 + p8 + p9 + p10 + p11 + p12 + p13 + p14 + p15 + p16 + plot_layout(ncol = 2)
#heights = c(3, 2, 2, 5, 3, 2, 2, 5, 2, 2, 2, 2, 3, 2, 2)
(p1 / p3 / p5 / p7 / p9 / p11 / p13 / p15) | (p2 / p4 / p6 / p8 / p10 / p12 / p14 / p16)

ggsave("plots/Figure6_Rplot.pdf", width = 12, height = 17, units = "cm", dpi = 300, scale=2.5)

#+ theme(legend.position = c(0.6, 1), legend.justification = c(0, 1), legend.key.size = unit(1, "mm")) + theme(legend.direction = "horizontal", legend.title = element_text(size = 8), legend.text = element_text(size = 8))
```


### Figure S3
Funnel plots


```{r Figure Funnels old, eval=FALSE, include = FALSe}
#Funnel plots for the estimated effect sizes for meta-analytic (intercept-only) models for the difference between better and worse treatments (*Hg*). 
#Positive values of *Hg* can be interpreted as animals in relatively better treatment group being more "optimistic"than animals in relatively worse treatment group. 
#Panel **A** is based on raw effect sizes and their precision (inversed square root of standard errors). Panel **B** is based on the residual values from the full meta-regression models, containing all moderators, and their precision.  

#rm(list=ls())
load(file="./Rdata/MR_Full_0.Rdata")


#dev.off()

pdf(file="plots/Figure_S3_funnels.pdf",width=8,height=4,family="sans",pointsize=10)
par(mfcol=c(1,2),mar=c(5,4,2,1.75),oma=c(1,2,1,0))

#raw data
plot(1/sqrt(dat$Vd) ~ dat$d, pch=16, xlim=c(-8,8), ylim=c(0,6),  xlab="Effect size [Hg]", ylab=expression("Precision  "(1/SE)),  main="", type="n") #raw
points(1/sqrt(dat$Vd) ~ dat$d, col=rgb(0, 0, 0, alpha=0.3), pch=16)
abline(v=0,lty=1)
abline(v=0.19,lty=3)
mtext("A", 3, 0, at=-11.3, cex=1.4, font=2)

#regressed residuals from the full model

funnel(MR_Full_0, yaxis = "seinv", level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), refline=0, legend=FALSE, xlim=c(-8,8), ylim=c(0.5,1.5), steps=3, xlab="Regressed residuals")
#plot(prec~es, xlim=c(-8,8), ylim=c(0,10), pch=16, xlab="Regressed residuals",	ylab=expression("Precision  "(1/SE)),  main="", type="n") #es values are from Eggers regression
#points(prec ~ es, col=rgb(0, 0, 0, alpha=0.3), pch=16)
#abline(v=0,lty=3)
mtext("B", 3, 0,at=-11.3, cex=1.4, font=2)

dev.off()
```





**********************************************************************************************************************

*********************************************************** OLD

## MA models for full data and 3 subsets - OLD - see below
```{r forestplot MA Models OLD, echo=FALSE}
res_MA <- read.csv("./Tables/Table MA_v3.csv", col.names=c("ES", "Dataset", "Intercept", "Mean", "CI.lb", "CI.ub", "RandomEffects", "S2", "k"), skip=2)
str(res_MA)
res_MA$k <- c(res_MA$k[4], rep(NA,4), res_MA$k[9], rep(NA,4), res_MA$k[14], rep(NA,4), res_MA$k[19], rep(NA,4), res_MA$k[24], rep(NA,3)) #transfer sample sizes values to the top row for each subset
res_MA <- dplyr::filter(res_MA, Mean != "NA") #get rid of redundant rows
res_MA$Signif <- ifelse(res_MA$CI.lb>0 | res_MA$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
res_MA$pch <- 20 #set font size
res_MA <- res_MA[dim(res_MA)[1]:1, ] #reverse order

pdf(file="plots/Fig_MA_models.pdf",width=6,height=4,pointsize=12)
par(mfcol=c(1,1))
#layout(matrix(1))
par(mar=c(4,4,1,0))
plot(res_MA$Mean, 1:length(res_MA$Mean), ylab=NA, yaxt="n", bty="n", xlim=c(-2,2), ylim=c(0.25, length(res_MA$Mean)+.5), xlab="effect size [Hg]", pch=res_MA$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(res_MA$Dataset[1:length(res_MA$Dataset)], side = 2, line = -3, at=1:length(res_MA$Dataset), las=2, cex=.8, font=3, outer = FALSE) #add dataset labels
#mtext(res_MA$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(res_MA$CI.lb, 1:length(res_MA$M), res_MA$CI.ub, 1:length(res_MA$M), lwd=1.25) #add whiskers for CI
for (i in 1:length(rownames(res_MA))) mtext(res_MA$Signif[i], side = 2, line = -5, at=i, las=2, cex=.7) #add stars
mtext(res_MA$k, 4, -2.8, at=1:(length(res_MA$k)), las=2, cex=.8, font=1, adj=1) #add k values
mtext("k", 4, -2.8, at=length(res_MA$k)+0.5, las=2, cex=.8, font=3, adj=1)

dev.off()
```



## MA models for full data and its 4 ES subsets, using "./Tables/Table_MA_v3_all.csv"

```{r forestplot MA Models all data, echo=FALSE}
res_MA <- read.csv("./Tables/Table_MA_v3_all.csv", col.names=c("ES", "Dataset", "Intercept", "Mean", "CI.lb", "CI.ub", "RandomEffects", "S2", "k", "X","row"), skip=2)
str(res_MA)
res_MA <- select(res_MA, - c(X, row)) #remove last 2 columns
res_MA <- slice(res_MA, 1:24) #remove empty rows at the bottom
res_MA$k <- c(res_MA$k[4], rep(NA,4), res_MA$k[9], rep(NA,4), res_MA$k[14], rep(NA,4), res_MA$k[19], rep(NA,4), res_MA$k[24], rep(NA,3)) #transfer sample sizes values to the top row for each subset
res_MA <- dplyr::filter(res_MA, Mean != "NA") #get rid of redundant rows
res_MA$Signif <- ifelse(res_MA$CI.lb>0 | res_MA$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
res_MA$pch <- 20 #set font size
res_MA <- res_MA[dim(res_MA)[1]:1, ] #reverse order

pdf(file="plots/Fig_MA_models.pdf",width=6,height=4,pointsize=12)
par(mfcol=c(1,1))
#layout(matrix(1))
par(mar=c(4,4,1,0))
plot(res_MA$Mean, 1:length(res_MA$Mean), ylab=NA, yaxt="n", bty="n", xlim=c(-2,2), ylim=c(0.25, length(res_MA$Mean)+.5), xlab="effect size [Hg]", pch=res_MA$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(res_MA$Dataset[1:length(res_MA$Dataset)], side = 2, line = -3, at=1:length(res_MA$Dataset), las=2, cex=.8, font=3, outer = FALSE) #add dataset labels
#mtext(res_MA$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(res_MA$CI.lb, 1:length(res_MA$M), res_MA$CI.ub, 1:length(res_MA$M), lwd=1.25) #add whiskers for CI
for (i in 1:length(rownames(res_MA))) mtext(res_MA$Signif[i], side = 2, line = -5, at=i, las=2, cex=.7) #add stars
mtext(res_MA$k, 4, -2.8, at=1:(length(res_MA$k)), las=2, cex=.8, font=1, adj=1) #add k values
mtext("k", 4, -2.8, at=length(res_MA$k)+0.5, las=2, cex=.8, font=3, adj=1)
title("All data")
dev.off()
```


## MA models for latency data and its 4 ES subsets, using "./Tables/Table_MA_v3_lat.csv"

```{r forestplot MA Models latency data, echo=FALSE}
res_MA_lat <- read.csv("./Tables/Table_MA_v3_lat.csv", col.names=c("ES", "Dataset", "Intercept", "Mean", "CI.lb", "CI.ub", "RandomEffects", "S2", "k", "X","row"), skip=2)
str(res_MA_lat)
res_MA_lat <- select(res_MA_lat, - c(X, row)) #remove last 2 columns
res_MA_lat <- slice(res_MA_lat, 1:24) #remove empty rows at the bottom
res_MA_lat$k <- c(res_MA_lat$k[4], rep(NA,4), res_MA_lat$k[9], rep(NA,4), res_MA_lat$k[14], rep(NA,4), res_MA_lat$k[19], rep(NA,4), res_MA_lat$k[24], rep(NA,3)) #transfer sample sizes values to the top row for each subset
res_MA_lat <- dplyr::filter(res_MA_lat, Mean != "NA") #get rid of redundant rows
res_MA_lat$Signif <- ifelse(res_MA_lat$CI.lb>0 | res_MA_lat$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
res_MA_lat$pch <- 20 #set font size
res_MA_lat <- res_MA_lat[dim(res_MA_lat)[1]:1, ] #reverse order

pdf(file="plots/Fig_MA_models_lat.pdf",width=6,height=4,pointsize=12)
par(mfcol=c(1,1))
#layout(matrix(1))
par(mar=c(4,4,1,0))
plot(res_MA_lat$Mean, 1:length(res_MA_lat$Mean), ylab=NA, yaxt="n", bty="n", xlim=c(-2,2), ylim=c(0.25, length(res_MA_lat$Mean)+.5), xlab="effect size [Hg]", pch=res_MA_lat$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(res_MA_lat$Dataset[1:length(res_MA_lat$Dataset)], side = 2, line = -3, at=1:length(res_MA_lat$Dataset), las=2, cex=.8, font=3, outer = FALSE) #add dataset labels
#mtext(res_MA_lat$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(res_MA_lat$CI.lb, 1:length(res_MA_lat$M), res_MA_lat$CI.ub, 1:length(res_MA_lat$M), lwd=1.25) #add whiskers for CI
for (i in 1:length(rownames(res_MA_lat))) mtext(res_MA_lat$Signif[i], side = 2, line = -5, at=i, las=2, cex=.7) #add stars
mtext(res_MA_lat$k, 4, -2.8, at=1:(length(res_MA_lat$k)), las=2, cex=.8, font=1, adj=1) #add k values
mtext("k", 4, -2.8, at=length(res_MA_lat$k)+0.5, las=2, cex=.8, font=3, adj=1)
title("Latency data")
dev.off()
```



## MA models for proportion data and its 4 ES subsets, using "./Tables/Table_MA_v3_prop.csv"

```{r forestplot MA Models proportion data, echo=FALSE}
res_MA_prop <- read.csv("./Tables/Table_MA_v3_prop.csv", col.names=c("ES", "Dataset", "Intercept", "Mean", "CI.lb", "CI.ub", "RandomEffects", "S2", "k", "X","row"), skip=2)
str(res_MA_prop)
res_MA_prop <- select(res_MA_prop, - c(X, row)) #remove last 2 columns
res_MA_prop <- slice(res_MA_prop, 1:24) #remove empty rows at the bottom
res_MA_prop$k <- c(res_MA_prop$k[4], rep(NA,4), res_MA_prop$k[9], rep(NA,4), res_MA_prop$k[14], rep(NA,4), res_MA_prop$k[19], rep(NA,4), res_MA_prop$k[24], rep(NA,3)) #transfer sample sizes values to the top row for each subset
res_MA_prop <- dplyr::filter(res_MA_prop, Mean != "NA") #get rid of redundant rows
res_MA_prop$Signif <- ifelse(res_MA_prop$CI.lb>0 | res_MA_prop$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
res_MA_prop$pch <- 20 #set font size
res_MA_prop <- res_MA_prop[dim(res_MA_prop)[1]:1, ] #reverse order

pdf(file="plots/Fig_MA_models_prop.pdf",width=6,height=4,pointsize=12)
par(mfcol=c(1,1))
#layout(matrix(1))
par(mar=c(4,4,1,0))
plot(res_MA_prop$Mean, 1:length(res_MA_prop$Mean), ylab=NA, yaxt="n", bty="n", xlim=c(-2,2), ylim=c(0.25, length(res_MA_prop$Mean)+.5), xlab="effect size [Hg]", pch=res_MA_prop$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(res_MA_prop$Dataset[1:length(res_MA_prop$Dataset)], side = 2, line = -3, at=1:length(res_MA_prop$Dataset), las=2, cex=.8, font=3, outer = FALSE) #add dataset labels
#mtext(res_MA_prop$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(res_MA_prop$CI.lb, 1:length(res_MA_prop$M), res_MA_prop$CI.ub, 1:length(res_MA_prop$M), lwd=1.25) #add whiskers for CI
for (i in 1:length(rownames(res_MA_prop))) mtext(res_MA_prop$Signif[i], side = 2, line = -5, at=i, las=2, cex=.7) #add stars
mtext(res_MA_prop$k, 4, -2.8, at=1:(length(res_MA_prop$k)), las=2, cex=.8, font=1, adj=1) #add k values
mtext("k", 4, -2.8, at=length(res_MA_prop$k)+0.5, las=2, cex=.8, font=3, adj=1)
title("Proportion data")
dev.off()
```




###################################################################
## MR interaction plot for Test Type vs.Measurement Type 
###################################################################

```{r forestplot MA Models, echo=FALSE}
res_MRi <- read.csv("./Tables/Table MR_TT_MT_i.csv", col.names=c("ES", "Dataset", "Intercept", "Test Type", "Measurement Type", "Mean" ,"CI.lb", "CI.ub", "k"), skip=2)
str(res_MRi)
#res_MRi <- dplyr::filter(res_MRi, Mean != "NA") #get rid of redundant rows
res_MRi$Signif <- ifelse(res_MRi$CI.lb>0 | res_MRi$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
res_MRi$pch <- 20 #set font size
#res_MRi <- res_MRi[dim(res_MRi)[1]:1, ] #reverse order


p1 <- ggplot(res_MRi[1:4,], aes(x=Measurement.Type, y=Mean, color= Test.Type, group=Test.Type)) + 
    geom_point() + 
    geom_line(size=1.2) +
    geom_ribbon(aes(ymin=CI.lb, ymax=CI.ub, fill= Test.Type),alpha=0.3) + 
    geom_hline(yintercept = 0, linetype="dashed") +
    labs(title = "A. All data", x= "Measurement type", y="Hg", color="Measurement.Type", fill="Measurement.Type") + theme_classic() + theme(text=element_text(size=10)) +
    theme(legend.position = c(0.2, 0.9)) +
    coord_cartesian(ylim = c(-0.6, 1.4))

p2 <- ggplot(res_MRi[7:10,], aes(x=Measurement.Type, y=Mean, color= Test.Type, group=Test.Type)) + 
    geom_point() + 
    geom_line(size=1.2) +
    geom_ribbon(aes(ymin=CI.lb, ymax=CI.ub, fill= Test.Type),alpha=0.3) + 
    geom_hline(yintercept = 0, linetype="dashed") +
    labs(title = "B. Max(Hg) subset", x= "Measurement type", y="Hg", color="Measurement.Type", fill="Measurement.Type") + theme_classic() + theme(text=element_text(size=10)) +
    theme(legend.position = c(0.2, 0.9)) +
    coord_cartesian(ylim = c(-0.6, 1.4))

p3 <- ggplot(res_MRi[13:16,], aes(x=Measurement.Type, y=Mean, color= Test.Type, group=Test.Type)) + 
    geom_point() + 
    geom_line(size=1.2) +
    geom_ribbon(aes(ymin=CI.lb, ymax=CI.ub, fill= Test.Type),alpha=0.3) + 
    geom_hline(yintercept = 0, linetype="dashed") +
    labs(title = "C. Max(abs(Hg)) subset", x= "Measurement type", y="Hg", color="Measurement.Type", fill="Measurement.Type") + theme_classic() + theme(text=element_text(size=10)) +
    theme(legend.position = c(0.2, 0.9)) +
    coord_cartesian(ylim = c(-0.6, 1.4))

p4 <- ggplot(res_MRi[19:22,], aes(x=Measurement.Type, y=Mean, color= Test.Type, group=Test.Type)) + 
    geom_point() + 
    geom_line(size=1.2) +
    geom_ribbon(aes(ymin=CI.lb, ymax=CI.ub, fill= Test.Type),alpha=0.3) + 
    geom_hline(yintercept = 0, linetype="dashed") +
    labs(title = "D. Dominant Hg subset", x= "Measurement type", y="Hg", color="Measurement.Type", fill="Measurement.Type") + theme_classic() + theme(text=element_text(size=10)) +
    theme(legend.position = c(0.2, 0.9)) +
    coord_cartesian(ylim = c(-0.6, 1.4))


#grid.arrange(p1, p2, p3, p4, ncol = 2, nrow = 2)

pdf(file="plots/Fig_MR_TT_MT_i.pdf",width=8,height=8,pointsize=12)
  grid.arrange(p1, p2, p3, p4, ncol = 2, nrow = 2)
dev.off()
```



## Species forest + phylogeny

```{r species plot}
### PLOT - species phylogeny and forest plot v2 (narrower)
# loading data
tree <- read.tree(file="tree_all.tre")
load("./Rdata/MR_all_species.Rdata") #with phylogeny
#load("./Rdata/MR_all_species2.Rdata") #without phylogeny
ssp <- MR_all_species
load("Rdata/MA_all.Rdata")
#gsub("ScientificName","",rownames(summary(MR_all_species)$b))
res_species_df <- data.frame(Model = substr(attr(ssp$b,"dimnames")[[1]], 15, 50), M = ssp$b, CI.lb = ssp$ci.lb, CI.ub = ssp$ci.ub, I2=NA, pch=20)
res_species_df <- res_species_df[match(tree$tip.label, res_species_df$Model), ] #reorder dataframe to match order of the tip labels on the tree
res_species_df$Signif <- ifelse(res_species_df$CI.lb>0 | res_species_df$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
count_animals <- data.frame(Model=names(table(dat$Species_Latin)), k=table(dat$Species_Latin)) #count how many ES per species
merged_res_species_df <- merge(res_species_df, count_animals, all=FALSE, sort=FALSE)
tab <- read.csv("tables/papers_table.csv")
table(tab$Species)
count_papers <- data.frame(Model=names(table(tab$Species)), K=table(tab$Species)) #count how many papers per species
merged_res_species_df2 <- merge(merged_res_species_df, count_papers, all=FALSE, sort=FALSE)
merged_res_species_df2 <- rbind(merged_res_species_df2, data.frame(Model=c("Meta-analytic mean "), M=MA_all$b[1], CI.lb=MA_all$ci.lb[1], CI.ub=MA_all$ci.ub[1], I2=NA, pch=18, Signif="", k.Var1 = NA, k.Freq=sum(merged_res_species_df2$k.Freq), K.Var1=NA, K.Freq=sum(merged_res_species_df2$K.Freq)))
write.csv(merged_res_species_df2,"tables/MR_species_res.csv")

pdf(file="plots/Fig_species_v2.pdf",width=6.5,height=6.5,pointsize=11)
layout(matrix(c(1,2),1), c(1,3), c(1,3))
par(mar=c(5.2,1,3.1,0))
plot(tree, font=1, cex=0.8, x.lim=1, show.tip.label = FALSE)
par(mar=c(4,7,1,0))
plot(merged_res_species_df2$M, 1:length(merged_res_species_df2$M), ylab=NA, yaxt="n", bty="n", xlim=c(-4,4), ylim=c(0.25, length(merged_res_species_df2$M)+.5), xlab="effect size [Hg]", pch=merged_res_species_df2$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(merged_res_species_df2$Model[1:length(merged_res_species_df2$Model)], 2, -1, at=1:length(merged_res_species_df2$Model), las=2, cex=.8, font=3)
#mtext(merged_res_species_df2$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(merged_res_species_df2$CI.lb, 1:length(merged_res_species_df2$M), merged_res_species_df2$CI.ub, 1:length(merged_res_species_df2$M), lwd=1.25)
for (i in 1:length(rownames(merged_res_species_df2))) mtext(merged_res_species_df2$Signif[i], 2, -1.5, at=i, las=2, cex=.7) #add stars
mtext(merged_res_species_df2$k.Freq, 4, -2.8, at=1:(length(merged_res_species_df2$k.Freq)), las=2, cex=.8, font=1, adj=1) #add k values
mtext(merged_res_species_df2$K.Freq, 4, -1.4, at=1:(length(merged_res_species_df2$K.Freq)), las=2, cex=.8, font=1, adj=1) #add K values
mtext("k", 4, -2.8, at=length(merged_res_species_df2$k.Freq)+1, las=2, cex=.8, font=1, adj=1)
mtext("K", 4, -1.4, at=length(merged_res_species_df2$K.Freq)+1, las=2, cex=.8, font=1, adj=1)
dev.off()

#NOTE: fine edit plot formatting in AdobeIllustrator (add pictograms)
```


```{r boxplot Sex vs MeasureType, echo=FALSE}
pdf(file="plots/Fig_boxplot_raw_Sex_MeasureType.pdf",width=11,height=5,pointsize=11)
boxplot(dat$d ~ dat$Sex + dat$MeasureType, ylab="effect size [Hg]", varwidth=TRUE)
abline(h=0, lty=3)
dev.off()
```


```{r single forestplot Full Model, echo=FALSE}
res_full <- read.csv("./Tables/Table S7.csv", col.names=c("names", "Levels.and.contrasts","Mean", "CI.lb", "CI.ub", "k"), skip=2)
str(res_full)
res_full$Signif <- ifelse(res_full$CI.lb>0 | res_full$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
res_full$k <- c(table(dat$Sex, dat$MeasureType),rep(NA,6))
res_full$pch <- 20
res_full$Levels.and.contrasts <- gsub(" – ", " vs. ", res_full$Levels.and.contrasts) 
res_full <- res_full[dim(res_full)[1]:1, ] #reverse order

pdf(file="plots/Fig_full_model.pdf",width=6,height=4,pointsize=12)
par(mfcol=c(1,1))
#layout(matrix(1))
par(mar=c(4,6,1,0))
plot(res_full$M, 1:length(res_full$M), ylab=NA, yaxt="n", bty="n", xlim=c(-2,2), ylim=c(0.25, length(res_full$M)+.5), xlab="effect size [Hg]", pch=res_full$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(res_full$Levels.and.contrasts[1:length(res_full$Levels.and.contrasts)], side = 2, line = -6, at=1:length(res_full$Levels.and.contrasts), las=2, cex=.8, font=3, outer = FALSE)
#mtext(res_full$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(res_full$CI.lb, 1:length(res_full$M), res_full$CI.ub, 1:length(res_full$M), lwd=1.25)
for (i in 1:length(rownames(res_full))) mtext(res_full$Signif[i], side = 2, line = -7, at=i, las=2, cex=.7) #add stars
mtext(res_full$k, 4, -2.8, at=1:(length(res_full$k)), las=2, cex=.8, font=1, adj=1) #add k values
mtext("k", 4, -2.8, at=length(res_full$k)+1, las=2, cex=.8, font=1, adj=1)

dev.off()
```

### Figure Funnels  


```{r Figure Funnels old, eval=FALSE, include = FALSe}
#Funnel plots for the estimated effect sizes for meta-analytic (intercept-only) models for the difference between better and worse treatments (*Hg*). 
#Positive values of *Hg* can be interpreted as animals in relatively better treatment group being more "optimistic"than animals in relatively worse treatment group. 
#Panel **A** is based on raw effect sizes and their precision (inversed square root of standard errors). Panel **B** is based on the residual values from the full meta-regression models, containing all moderators, and their precision.  

#rm(list=ls())
load("Rdata/MA_all.Rdata")
load(file="Rdata/residuals_Prec.RData") #loads es and Prec for residuals
load(file="Rdata/bayesian_runs_full1.RData") #m1: bayesian_full1.1
model <- bayesian_full1.1

pdf(file="plots/Figure_funnels.pdf",width=8,height=4,family="sans",pointsize=10)
par(mfcol=c(1,2),mar=c(5,4,2,1.75),oma=c(1,2,1,0))

#raw data
ES <- dat$d
VES <- dat$Vd
prec <- 1/sqrt(VES)
plot(prec~ES, pch=16, xlim=c(-8,8), ylim=c(0,10),  xlab="Effect size [Hg]", ylab=expression("Precision  "(1/SE)),  main="", type="n") #raw
points(prec~ES, col=rgb(0, 0, 0, alpha=0.3), pch=16)
abline(v=0,lty=3)
mtext("A",3,0,at=-12, cex=1.4, font=2)

#regressed residuals
plot(prec~es, xlim=c(-8,8), ylim=c(0,10), pch=16, xlab="Regressed residuals",	ylab=expression("Precision  "(1/SE)),  main="", type="n") #es values are from Eggers regression
points(prec~es, col=rgb(0, 0, 0, alpha=0.3), pch=16)
abline(v=0,lty=3)
mtext("B",3,0,at=-12, cex=1.4, font=2)

dev.off()
```





###############################################################################################################
###########################################        SUBSET - max ES per study        ########################################### 
###############################################################################################################


```{r subset data max ES} 
dim(dat) #265 70
names(dat)

# View(tbl_df(dat) %>% group_by(ExperimentID, MeasureType, GroupID, ComparisonCategory, Sex) %>% summarise_at("d", funs(n())) ) #how many rows within each group 105, 121 129

dat_max <- tbl_df(dat) %>% group_by(ExperimentID, MeasureType, GroupID, ComparisonCategory, Sex) %>% summarise_at("d", funs(max(., na.rm = TRUE))) #which d value is max within each group
dat_max$d
#hist(dat_max$d)
dim(dat_max) #107
unique(dat_max$d) #all 107 - can use to merge back

dat_max_merged <- dplyr::inner_join(dat, dat_max, by = c("ExperimentID","MeasureType","GroupID","ComparisonCategory", "Sex","d"))

dim(dat_max_merged)
names(dat_max_merged)
#View(dat_max_merged)

dat_max <- dat_max_merged
str(dat_max)

## prepare VCV matrix - all data
VCV_max <- make_VCV_matrix(data = dat_max, V = "Vd", cluster = "GroupID", obs = "EffectID")
```


## Species forest + phylogeny

```{r species plot max}
### PLOT - species phylogeny and forest plot v2 (narrower)
# loading data
tree <- read.tree(file="tree_all.tre")
load("./Rdata/MR_all_max_species.Rdata") #with phylogeny
#load("./Rdata/MR_all_species2.Rdata") #without phylogeny
ssp <- MR_all_max_species
load("Rdata/MA_all_max.Rdata")
MA <- MA_all_max
#gsub("ScientificName","",rownames(summary(MR_all_species)$b))
res_species_df <- data.frame(Model = substr(attr(ssp$b,"dimnames")[[1]], 15, 50), M = ssp$b, CI.lb = ssp$ci.lb, CI.ub = ssp$ci.ub, I2=NA, pch=20)
res_species_df <- res_species_df[match(tree$tip.label, res_species_df$Model), ] #reorder dataframe to match order of the tip labels on the tree
res_species_df$Signif <- ifelse(res_species_df$CI.lb>0 | res_species_df$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
count_animals <- data.frame(Model=names(table(dat_max$Species_Latin)), k=table(dat_max$Species_Latin)) #count how many ES per species
merged_res_species_df <- merge(res_species_df, count_animals, all=FALSE, sort=FALSE)
tab <- read.csv("tables/papers_table.csv")
table(tab$Species)
count_papers <- data.frame(Model=names(table(tab$Species)), K=table(tab$Species)) #count how many papers per species
merged_res_species_df2 <- merge(merged_res_species_df, count_papers, all=FALSE, sort=FALSE)
merged_res_species_df2 <- rbind(merged_res_species_df2, data.frame(Model=c("Meta-analytic mean "), M=MA$b[1], CI.lb=MA$ci.lb[1], CI.ub=MA$ci.ub[1], I2=NA, pch=18, Signif="", k.Var1 = NA, k.Freq=sum(merged_res_species_df2$k.Freq), K.Var1=NA, K.Freq=sum(merged_res_species_df2$K.Freq)))
write.csv(merged_res_species_df2,"tables/MR_species_res_max.csv")

pdf(file="plots/Fig_species_max_v2.pdf",width=6.5,height=6.5,pointsize=11)
layout(matrix(c(1,2),1), c(1,3), c(1,3))
par(mar=c(5.2,1,3.1,0))
plot(tree, font=1, cex=0.8, x.lim=1, show.tip.label = FALSE)
par(mar=c(4,7,1,0))
plot(merged_res_species_df2$M, 1:length(merged_res_species_df2$M), ylab=NA, yaxt="n", bty="n", xlim=c(-4,4), ylim=c(0.25, length(merged_res_species_df2$M)+.5), xlab="effect size [Hg]", pch=merged_res_species_df2$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(merged_res_species_df2$Model[1:length(merged_res_species_df2$Model)], 2, -1, at=1:length(merged_res_species_df2$Model), las=2, cex=.8, font=3)
#mtext(merged_res_species_df2$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(merged_res_species_df2$CI.lb, 1:length(merged_res_species_df2$M), merged_res_species_df2$CI.ub, 1:length(merged_res_species_df2$M), lwd=1.25)
for (i in 1:length(rownames(merged_res_species_df2))) mtext(merged_res_species_df2$Signif[i], 2, -1.5, at=i, las=2, cex=.7) #add stars
mtext(merged_res_species_df2$k.Freq, 4, -2.8, at=1:(length(merged_res_species_df2$k.Freq)), las=2, cex=.8, font=1, adj=1) #add k values
mtext(merged_res_species_df2$K.Freq, 4, -1.4, at=1:(length(merged_res_species_df2$K.Freq)), las=2, cex=.8, font=1, adj=1) #add K values
mtext("k", 4, -2.8, at=length(merged_res_species_df2$k.Freq)+1, las=2, cex=.8, font=1, adj=1)
mtext("K", 4, -1.4, at=length(merged_res_species_df2$K.Freq)+1, las=2, cex=.8, font=1, adj=1)
dev.off()

#NOTE: fine edit plot formatting in AdobeIllustrator (add pictograms)
```



```{r boxplot Sex vs MeasureType, echo=FALSE}
pdf(file="plots/Fig_boxplot_raw_Sex_MeasureType_max.pdf",width=11,height=5,pointsize=11)
boxplot(dat_max$d ~ dat_max$Sex + dat_max$MeasureType, ylab="effect size [Hg]", varwidth=TRUE)
abline(h=0, lty=3)
dev.off()
```


```{r forestplot Full Model max, echo=FALSE}
res_full <- read.csv("./Tables/Table S7 max.csv", col.names=c("names", "Levels.and.contrasts","Mean", "CI.lb", "CI.ub", "k"), skip=2)
str(res_full)
res_full$Signif <- ifelse(res_full$CI.lb>0 | res_full$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
res_full$k <- c(table(dat_max$Sex, dat_max$MeasureType),rep(NA,6))
res_full$pch <- 20
res_full$Levels.and.contrasts <- gsub(" – ", " vs. ", res_full$Levels.and.contrasts) 
res_full <- res_full[dim(res_full)[1]:1, ] #reverse order

pdf(file="plots/Fig_full_model_max.pdf",width=6,height=4,pointsize=12)
par(mfcol=c(1,1))
#layout(matrix(1))
par(mar=c(4,6,1,0))
plot(res_full$M, 1:length(res_full$M), ylab=NA, yaxt="n", bty="n", xlim=c(-2,2), ylim=c(0.25, length(res_full$M)+.5), xlab="effect size [Hg]", pch=res_full$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(res_full$Levels.and.contrasts[1:length(res_full$Levels.and.contrasts)], side = 2, line = -6, at=1:length(res_full$Levels.and.contrasts), las=2, cex=.8, font=3, outer = FALSE)
#mtext(res_full$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(res_full$CI.lb, 1:length(res_full$M), res_full$CI.ub, 1:length(res_full$M), lwd=1.25)
for (i in 1:length(rownames(res_full))) mtext(res_full$Signif[i], side = 2, line = -7, at=i, las=2, cex=.7) #add stars
mtext(res_full$k, 4, -2.8, at=1:(length(res_full$k)), las=2, cex=.8, font=1, adj=1) #add k values
mtext("k", 4, -2.8, at=length(res_full$k)+1, las=2, cex=.8, font=1, adj=1)

dev.off()
```

### Figure Funnels  
Funnel plots for the estimated effect sizes for meta-analytic (intercept-only) models for the difference between better and worse treatments (*Hg*). 
Positive values of *Hg* can be interpreted as animals in relatively better treatment group being more "optimistic"than animals in relatively worse treatment group. 
Panel **A** is based on raw effect sizes and their precision (inversed square root of standard errors). Panel **B** is based on the residual values from the full meta-regression models, containing all moderators, and their precision.  

#TODO
```{r Figure Funnels}
#rm(list=ls())
load("Rdata/MA_all_max.Rdata")
load(file="Rdata/residuals_Prec.RData") #loads es and Prec for residuals
load(file="Rdata/bayesian_runs_full1.RData") #m1: bayesian_full1.1
model <- bayesian_full1.1

pdf(file="plots/Figure_funnels.pdf",width=8,height=4,family="sans",pointsize=10)
par(mfcol=c(1,2),mar=c(5,4,2,1.75),oma=c(1,2,1,0))

#raw data
ES <- dat$d
VES <- dat$Vd
prec <- 1/sqrt(VES)
plot(prec~ES, pch=16, xlim=c(-8,8), ylim=c(0,10),  xlab="Effect size [Hg]", ylab=expression("Precision  "(1/SE)),  main="", type="n") #raw
points(prec~ES, col=rgb(0, 0, 0, alpha=0.3), pch=16)
abline(v=0,lty=3)
mtext("A",3,0,at=-12, cex=1.4, font=2)

#regressed residuals
plot(prec~es, xlim=c(-8,8), ylim=c(0,10), pch=16, xlab="Regressed residuals",	ylab=expression("Precision  "(1/SE)),  main="", type="n") #es values are from Eggers regression
points(prec~es, col=rgb(0, 0, 0, alpha=0.3), pch=16)
abline(v=0,lty=3)
mtext("B",3,0,at=-12, cex=1.4, font=2)

dev.off()
```


###################################################
# Univariate models - all data
###################################################

```{r forestplot Univariate Models - all data, echo=FALSE}
res_univ_all <- read.csv("./Tables/Table_MR_univ_all.csv", col.names=c("Moderator", "Levels.and.contrasts","Mean", "CI.lb", "CI.ub","x.1", "x.2", "x.3"), skip=1) 
str(res_univ_all)
res_univ_all$Signif <- ifelse(res_univ_all$CI.lb>0 | res_univ_all$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
res_univ_all$pch <- 20
res_univ_all$Levels.and.contrasts <- gsub(" – ", " vs. ", res_univ_all$Levels.and.contrasts) 
res_univ_all$Levels.and.contrasts <- gsub(" intercept", "", res_univ_all$Levels.and.contrasts) 
res_univ_all$Levels.and.contrasts <- gsub(" contrast", "", res_univ_all$Levels.and.contrasts) 
res_univ_all <- res_univ_all[dim(res_univ_all)[1]:1, ] #reverse order

pdf(file="plots/Fig_univ_model_all.pdf",width=8,height=12,pointsize=10)
par(mfcol=c(1,1))
#layout(matrix(1))
par(mar=c(4,7,1,0))
plot(res_univ_all$Mean, 1:length(res_univ_all$Mean), ylab=NA, yaxt="n", bty="n", xlim=c(-2,2), ylim=c(0.25, length(res_univ_all$Mean)+.5), xlab="effect size [Hg]", pch=res_univ_all$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(res_univ_all$Moderator[1:length(res_univ_all$Moderator)], side=2, line=7, at=1:length(res_univ_all$Moderator), las=2, cex=.8, font=2, adj=0, outer=FALSE)
mtext(res_univ_all$Levels.and.contrasts[1:length(res_univ_all$Levels.and.contrasts)], side=2, line=6, at=1:length(res_univ_all$Levels.and.contrasts), las=2, cex=.8, font=3, adj=0, outer=FALSE)
segments(res_univ_all$CI.lb, 1:length(res_univ_all$Mean), res_univ_all$CI.ub, 1:length(res_univ_all$Mean), lwd=1.25)
for (i in 1:length(rownames(res_univ_all))) mtext(res_univ_all$Signif[i], side = 2, line = 6.2, at=i, las=2, cex=.7) #add stars
title("All data")
#mtext(res_univ_all$k, 4, -2.8, at=1:(length(res_univ_all$k)), las=2, cex=.8, font=1, adj=1) #add k values
#mtext("k", 4, -2.8, at=length(res_univ_all$k)+1, las=2, cex=.8, font=1, adj=1)
#add overall MA mean?
dev.off()
```


```{r forestplot Univariate Models - all data max_absES, echo=FALSE}
res_univ_max_absES <- read.csv("./Tables/Table_MR_univ_all_max_absES.csv", col.names=c("Moderator", "Levels.and.contrasts","Mean", "CI.lb", "CI.ub","x.1", "x.2", "x.3"), skip=1) 
str(res_univ_max_absES)
res_univ_max_absES$Signif <- ifelse(res_univ_max_absES$CI.lb>0 | res_univ_max_absES$CI.ub<0, "*", "") #add column with stars for estimates that significantly differ from zero
#res_univ_max_absES$k <- c(table(dat$Sex, dat$MeasureType),rep(NA,6))
res_univ_max_absES$pch <- 20
res_univ_max_absES$Levels.and.contrasts <- gsub(" – ", " vs. ", res_univ_max_absES$Levels.and.contrasts) 
res_univ_max_absES$Levels.and.contrasts <- gsub(" intercept", "", res_univ_max_absES$Levels.and.contrasts) 
res_univ_max_absES$Levels.and.contrasts <- gsub(" contrast", "", res_univ_max_absES$Levels.and.contrasts) 
res_univ_max_absES <- res_univ_max_absES[dim(res_univ_max_absES)[1]:1, ] #reverse order

pdf(file="plots/Fig_univ_model_all_max_absES.pdf",width=6,height=12,pointsize=10)
par(mfcol=c(1,1))
#layout(matrix(1))
par(mar=c(4,7,1,0))
plot(res_univ_max_absES$Mean, 1:length(res_univ_max_absES$Mean), ylab=NA, yaxt="n", bty="n", xlim=c(-2,2), ylim=c(0.25, length(res_univ_max_absES$Mean)+.5), xlab="effect size [Hg]", pch=res_univ_max_absES$pch, cex=1.5, cex.axis=.9, xaxp=c(-1, 1, 4) )
abline(v=0,lty=3)
mtext(res_univ_max_absES$Moderator[1:length(res_univ_max_absES$Moderator)], side=2, line=7, at=1:length(res_univ_max_absES$Moderator), las=2, cex=.8, font=2, adj=0, outer=FALSE)

mtext(res_univ_max_absES$Levels.and.contrasts[1:length(res_univ_max_absES$Levels.and.contrasts)], side=2, line=6, at=1:length(res_univ_max_absES$Levels.and.contrasts), las=2, cex=.8, font=3, adj=0, outer=FALSE)

#mtext(res_univ_max_absES$Model[1:2], 2, -1, at=1:2, las=2, cex=.8, font=1)
segments(res_univ_max_absES$CI.lb, 1:length(res_univ_max_absES$Mean), res_univ_max_absES$CI.ub, 1:length(res_univ_max_absES$Mean), lwd=1.25)
for (i in 1:length(rownames(res_univ_max_absES))) mtext(res_univ_max_absES$Signif[i], side = 2, line = 6.2, at=i, las=2, cex=.7) #add stars
title("All data Max(abs(ES)) subset")
#mtext(res_univ_max_absES$k, 4, -2.8, at=1:(length(res_univ_max_absES$k)), las=2, cex=.8, font=1, adj=1) #add k values
#mtext("k", 4, -2.8, at=length(res_univ_max_absES$k)+1, las=2, cex=.8, font=1, adj=1)
#add overall MA mean?
dev.off()
```

